---
title: "Coding Exercises"
author: "Taia Storrs"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
data("knz_bison")
```

Create a new column in the bison dataset that calculates the individual’s age at the time of observation.

```{r}
knz_bison <- knz_bison %>%
  mutate(age = rec_year - animal_yob)
```

Write a function that will first filter the bison dataset based on any user-specified weight threshold (returning the filtered dataset).

```{r}
bison_weight <- function(knz_bison, weight_threshold) {
  filtered_data <- knz_bison %>%
    filter(animal_weight > weight_threshold)
  
   return(filtered_data)
}
```

Example
```{r}
bison_over_600 <- bison_weight(knz_bison, 600)
```

Create a boxplot showing weight distribution between male and female bison, and then conduct a t-test to see if weight is significantly difference between males and females.

```{r}
ggplot(knz_bison, aes(x = animal_sex, y = animal_weight, fill = animal_sex)) +
  geom_boxplot() +
  labs(
    x = "Sex",
    y = "Weight (kg)"
  ) +
  scale_fill_manual(values = c("M" = "goldenrod2", "F" = "slateblue")) +
  theme_minimal()
```

